%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Huawei Technologies Canada} % Organization
    {Markham, ON, Canada} % Location
    {May 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with a team of architects and engineers to develop a distributed database management system ready for use in 5G networks.}
        \item {Optimized storage and transactional aspects of a distributed database system, and made server-side modifications to fix and improve the efficiency of client-server database transactions.}
        \item {Assessed and evaluated functionality of database queries and transactions; uncovered, reproduced, and repaired underlying issues in database, and provided tests for these issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer Engineering Research Assistant} % Job title
    {Holland Bloorview Kids Rehabilitation Hospital} % Organization
    {Toronto, ON, Canada} % Location
    {May 2019 - Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, tested and implemented a data acquisition / biofeedback system capable of measuring and improving gait in lower limb amputees.}
        \item {Implemented a program to efficiently sort and analyze data returned from a biofeedback system.}
        \item {Developed algorithm to make accurate interpretations of readings from force sensing resistors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Biomedical Engineering Research Assistant} % Job title
    {Holland Bloorview Kids Rehabilitation Hospital} % Organization
    {Toronto, ON, Canada} % Location
    {May 2018 - Aug 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed/measured parameters of gait in lower limb amputees and able bodied individuals.}
        \item {Proposed/developed methods of biofeedback based on measured gait parameters.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
